\chapter*{Acknowledgements}
\markboth{Acknowledgements}{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

\bigskip
% put your text here
\paragraph{}
First and foremost, I would like to address my wholehearted thanks to Professor Stephan Morgenthaler who accepted to be the supervisor of my master thesis project. His guidance was steady throughout the project. At the same time, he left me free to go into and explore many different directions. As a consequence, I have learnt many things, and the need to work efficiently and set priorities prominent amongst them.
\paragraph{}
I am most grateful to Doctor Olivier Lévêque (EPFL) for his excellent stochastic calculus course as well as the exercises that go with it. In my opinion, this material is nothing short of the best for anyone who wants to get a grasp of the topic. He was always available whenever I had a question, and I want to thank him for that too.
\paragraph{}
My most sincere thanks go to Professor Joseph Gergaud, the head of the Applied Mathematics \& Computer Science at ENSEEIHT, for allowing me to extend my exchange at EPFL and to pursue my master thesis project there.
\paragraph{}
Doctor Aurélie Hurault and Mrs Coralie Link, from the Student Exchange teams of ENSEEIHT and EPFL respectively, were there to answer my questions whenever they arose. Their support was very helpful throughout my time as an exchange student at EPFL, and I want to thank them for that.
\paragraph{}
Finally, I seize this opportunity to tell my friends and my family how much I am beholden to them !
\bigskip
 
\noindent\textit{Lausanne, 14 Ao\^{u}t 2015}
\hfill Killian Martin--Horgassan
