\chapter*{Preface}
\markboth{Preface}{Preface}
\addcontentsline{toc}{chapter}{Preface}

\bigskip
% put your text here
\paragraph{}
I am currently a third-year engineering student at ENSEEIHT, a French 'Grande Ecole d'Ingénieurs' located in Toulouse. Like most students in my class, my first two years of higher education were spent in a 'Classe Prépa Maths Sup-Maths Spé'. There, I began to acquaint myself with advanced mathematics. It was mainly theoretical mathematics, and a good foundation upon which build further knowledge and skills. \newline Then, I passed a competitive entrance exam and I became an Applied Mathematics \& Computer Science  engineering student at ENSEEIHT. My training there took a more practical dimension, as the problems we were asked to solve were closer to those encountered in real life. My life took a turn - from the academic perspective at least - when I came across two books : \underline{Options, Futures and Other Derivatives} by John C. Hull and \underline{The Signal and the Noise} by Nate Silver. I had always had an interest in Finance, and then I realised that I was woefully ignorant of probability, statistics and stochastic calculus. Not only would I need them in my professional life, they were fascinating branches of Mathematics as well !
\paragraph{}
I set out to right that wrong and remedy this issue ; during my first semester as an exchange student at EPFL I took courses in those fields. It was not always easy but whatever difficulties I encountered only fed my interest in the subjects. I was given the opportunity to extend my exchange at EPFL to do a master thesis project under the supervision of Prof. Stephan Morgenthaler. I could not quite make up my mind between statistics and finance, and that is why I decided to do my master thesis project on extreme value statistics applied to finance. Extreme value statistics is very different from the kind of statistics I had so far encountered, and from the early days of the project I realised that the topic I had picked was vast. It may be that I shall have only scratched the surface of it at the end of the project. In any case, this project has been a good introduction to extreme value statistics and a incentive to explore further the field of financial mathematics !




\bigskip
 
\noindent\textit{Lausanne, 14 Ao\^{u}t 2015}
\hfill Killian Martin--Horgassan
