\appendix
\chapter*{Recommendations on the use of the bibliography}
\addcontentsline{toc}{chapter}{Recommendations on the use of the bibliography}
\markboth{Recommendations on the use of the bibliography}{Recommendations on the use of the bibliography}
%\chapter{An appendix}
\paragraph{\\[25 pt]}
First and foremost, it must be said that \textbf{all the books included in the Bibliography section are good books} (I will focus on the books dealing with Extreme Value Theory ; the book on R programming is a very fine one though, with a nice hands-on approach). However, \textbf{they may not be intended for the same uses and the same users}. I am giving my opinion on those books in case someone chances upon the repository and they want to learn more about Extreme Value Theory. \textbf{It is only my opinion, nothing more.}
\begin{itemize}
	\item \underline{An Introduction to Statistical Modelling of Extreme Values}, by Stuart Coles (Springer) is not surprisingly an introductory book; most of the time, at best a sketch of the proof is given. It may be best used in conjunction with a traditional course given by a teacher that will go more in-depth themselves. I would not recommend it as a primary source for a master thesis project, however.
	\item \underline{Statistics of Extremes, Theory and Applications}, by Beirlant, Goegebeur, Segers and Teugels (Wiley) is a balanced book, going enough into details. It is thus fit as a source for a master thesis project. The only thing going against it is the following : many figures to illustrate what is being explained is a good thing, but it would have been nice to detail a bit more the derivations of the proofs, at times.
	\item \underline{Modelling extremal events for Insurance and Finance}, by Embrechts, Kluppelberg and Mikosch (Springer) is nothing short of a summa. It is extremely detailed and thorough. I would not recommend it, however, as a source for a master thesis project as it would be a bit too ambitious to use it for that purpose. If you have more time and are ready for an involved reading, all the more so if you are interested in the financial applications of Extreme Value Theory, search for a companion no further!
\end{itemize}
